POMDP comparisons across sigma_m, sigma_g

### 2017-10-09 appendix/appendixB.Rmd
tweaking appendixB

```{r}
pars <- examples %>% 
  group_by(commonname) %>% 
  summarise(N = max(SSB)) %>% 
  right_join(meta)
```

@@

```{r}
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))

ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% 
  ungroup() 
ex
```

@@

Plot

@@

             who <- ex$commonname == meta[.z,"commonname"]
             df <- ex[who,]

             hindcast_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                            obs = index(df$scaled_biomass, states), 
                            action = index(df$scaled_catch,states),
                            alpha = .y)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario") %>% left_join(meta)
```
```{r}
rescale <- function(x) states[x]

pomdp_sims %>% 
  select(time, obs, action, optimal, commonname, sigma_m) %>%
  mutate_at(c("action", "optimal"), rescale) %>%
  ggplot(aes(time, optimal, col=as.character(sigma_m))) + 
  geom_line() + 
  geom_line(aes(time, action), col="black") +
  facet_wrap(~commonname, scales="free") 
```

>>>>

```{r}
pars <- examples %>% 
  group_by(commonname) %>% 
  summarise(N = max(SSB)) %>% 
  right_join(
    meta %>% 
      select(commonname, r, K) %>% 
      distinct())
```

@@

```{r}
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))
## repeats each series for each static model
ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% 
  ungroup() 
ex
```

@@

## Plots

@@

             ## FIXME need to get obs for unique commmonname, wrong length?
             who <- (ex$commonname == meta[.z,"commonname"]) 
             df <- ex[who,]

             hindcast_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                            obs = index(df$scaled_biomass, states), 
                            action = index(df$scaled_catch,states),
                            alpha = .y)$df %>% 
              mutate(method = "pomdp") %>% # include a column labeling method
              mutate(year = ex[who, "year"][[1]]) 
           },
           .id = "scenario") 
```

```{r}
pomdp_sims <- 
  meta %>% 
  select(scenario, commonname,sigma_m) %>% 
  left_join(pars) %>%
  right_join(pomdp_sims)

```{r}
sims <- pomdp_sims %>% 
  mutate(optimal = states[optimal] * N) %>% # original scale
  select(year, optimal, commonname, sigma_m) %>%
  rename(stock = optimal) %>% 
  ## treat each sigma_m value as separate 'model'
  mutate(sigma_m = as.factor(sigma_m)) %>%
  mutate(model = recode(sigma_m, 
                        "0" = "reed",
                        "0.1" = "pomdp_0.1", 
                        "0.2" = "pomdp_0.2")) %>%
  select(-sigma_m) %>%
  bind_rows(historical)
```

```{r}
sims %>%
  filter(model %in% c("biomass", "catch", "pomdp_0.2", "reed", "pgy")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", "#D9661F", "#FDB515", "#6C3302", "#00B0DA", "#CFDD45", "#3B7EA1")) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```
